Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2023-04-17 writing/XPRAG-abstract/XPRAG-abstract.tex
added XPRAG abstract

\documentclass[12pt, a4paper]{article}

@@

% \usepackage{euler} % math font package needs to be loaded before others
\usepackage{xunicode,xltxtra, polyglossia}
\setdefaultlanguage[variant=american]{english}

@@

%% decoration and features
%%% colors
\usepackage[dvipsnames]{xcolor}

%% fonts
	\setmainfont[Scale=MatchLowercase,Mapping=tex-text, SmallCapsFeatures={Letters=SmallCaps}]{Times New Roman}
	\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Times New Roman}
	\setmonofont[Scale=MatchLowercase]{Andale Mono}

@@

\begin{center}
	\textbf{\large%\thetitle
		Projection variability of attitude complements across different operators}
\end{center}

\vspace{-.8\baselineskip}
\noindent 
	We present experimental evidence that the projection of the content of attitude complements \textbf{(i)} varies between entailment-canceling operators, and \textbf{(ii)} that this by-operator variation differs between attitude predicates.
	%
	The observed variability is not captured by existing theoretical accounts of projection
	(e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992,abrusan_predicting_2011,schlenker_triggering_2021}).
	%
	Our results suggest that an analysis must consider interactions between predicates and operators and raise important questions for future research on projection.

\noindent {\bf Projection across entailment-cancelling operators.}
	Language users may infer that a speaker who utters an attitude ascription, as in \ref{ex:family}, is committed to the content of the complement (CC, here: \emph{Julian dances salsa,})
	even when it occurs under an entailment-canceling operator, like negation \ref{ex:neg}, polar questions \ref{ex:q}, modals \ref{ex:mod}, or conditionals \ref{ex:cond}, in which case we say that it \emph{projects}.

	\vspace{-.5\baselineskip}
	\ex. \label{ex:family}
		\a. \label{ex:neg}
			{\bf Negation:} \hfill
			\emph{\lq Cole didn't discover that Julian dances salsa.\rq}
		\b. \label{ex:q}
			{\bf Polar Question:} \hfill
			\emph{\lq Did Cole discover that Julian dances salsa?\rq}
		\c. \label{ex:mod}
			{\bf Modal:} \hfill
			\emph{\lq Perhaps Cole discovered that Julian dances salsa.\rq}
		\d. \label{ex:cond}
			{\bf Conditional:} \hfill
			\emph{\lq If Cole discovered that Julian dances salsa, Logan will be joyful.\rq}
		\z.
	\z.

	\vspace{-.5\baselineskip}
	\noindent  Current research rarely examines projection variability across these operators, with conflicting findings.
	%
	\citet{karttunen_observations_1971} proposed a distinction between English factive predicates (e.g., \emph{be annoyed, regret}), where the CC projects across all four operators, and semi-factives (e.g., \emph{discover, realize, see, notice}) where it always projects across negation, but not always for the other operators.
	%
	Comparing different types of contents, \citet{smith_relationship_2014} found that the projective content of epithets and the CC of \emph{know} was more projective under negation than conditionals,
	whereas that of non-restrictive relative clauses and \emph{win} showed the opposite pattern.
	%
	This result was replicated for German \emph{wissen} `know' in \posscite{sieker_projective_2022} study on German attitude predicates, but as part of an overall pattern of higher projection ratings with negation than other operators. They found no interaction with predicate type, or evidence for the distinction of factives vs. semi-factives.

	These studies raise the question if the divergent results are due to cross-linguistic variation, task differences, or different contents being tested. To address this, we conducted a series of experiments designed to assess projection across the four entailment-canceling operators in \ref{ex:family}. We used the same projection measure as \citet{sieker_projective_2022} (the `certain that' diagnostic; see e.g., \citealp{tonhauser_how_2018,djarv_prosodic_2017,mahler_social_2020}) and applied it to the CC of 20 English clause-embedding predicates, including factive (\emph{be annoyed, know, reveal}) and semi-factive predicates (\emph{discover, see}),
	and 15 non-factive predicates, given recent findings that their complements may also project, albeit to varying degrees (\citealt{degen_are_2022}).

\noindent 
{\bf Method.}
	Projection of the CC of the 20 attitude predicates was measured in four sets of experiments: The predicates were embedded in polar questions in Exps.\ 1, under negation (Exps.\ 2), under {\em perhaps} (Exps.\ 3), and in conditional antecedents (Exps.\ 4). (Each set contained three experiments using different at-issueness measure in a separate block. Here, we focus on the projection ratings.)
	%
	In each experiment, participants read utterances like those in \ref{ex:family} and judged whether the speaker (who was named) was certain of the CC (e.g.: Is [the speaker] certain that Julian dances salsa?). Participants gave their response on a slider marked `no' (coded as 0) at one end and and `yes' (coded as 1) on the other. Each participant saw all 20 attitude predicates (each paired with a unique content from a set of 20 contents) under one operator. We analyze data from 2,682 self-reported native speakers of American English recruited on Prolific or Amazon's MT platform.
	% Based on Karttunen's generalization, we would expect the CC of semi-factive predicates to receive high projection ratings under negation and lower ratings under the other operators, while the CC of factive predicates would consistently receive relatively high projection ratings throughout.

\noindent
{\bf Results and Analysis.}
	Our analysis reveals two key results: \textbf{(i)} There is projection variability by operator. Mean projection ratings were higher under question-embeddings (Maximum likelihood estimate: $0.51$) than under negation (MLE: $0.48$) and modals ($0.47$), but lower than in conditional antecedents ($0.56$, see model \#1 in Table\ \ref{t:models}).
	%
	This result differs from that of \cite{sieker_projective_2022}, who observed that the CC of German attitude predicates projects more from under negation than the other operators.
	%
	\textbf{(ii)} There is by-predicate variation in the effect of operator on projection. This is illustrated in Figure~\ref{fig:figure1}, which shows mean projection ratings for the 20 attitude predicates by operator; predicates are ordered by their mean rating across all operators (\emph{be annoyed} has the highest overall mean).
	%
	For instance, the CC of \emph{be annoyed} projects more from under negation and questions than conditionals and modals, and the CC of \emph{discover} projects less from negation than conditionals and questions, and more from under negation than modals. The CC of \emph{know} projects less from under negation than questions, but more from under negation than modals, while the difference between negation and conditionals is not significant.
	%
	These generalizations are supported by models\ \# 2--4 in Table\ \ref{t:models}, which also each have at least $34$ highly significant interaction terms (out of $57$ possible interactions of operator and predicate).
	%
	%
	This result that by-operator projection variability interacts with predicate concurs with \citet{smith_relationship_2014}, while we did not reproduce their result that the CC of \emph{know} projects more from negation than conditionals. This differs from the result of \citet{sieker_projective_2022}, who found no interaction between predicates and operators.
	%
	Given that the methods and the set of projective contents of our experiment were very similar to theirs, this difference may suggest cross-linguistic variation in projection variability (cf. \citealt{tonhauser_projection_2020}).
	%
	On the other hand, in line with \citet{sieker_projective_2022}, our results are contrary to what would be expected based on \posscite{karttunen_observations_1971} distinction between factive and semi-factive predicates: The CC of (factive) \emph{be annoyed} does not project invariably from all four operators, and the CC of \emph{discover,}  which is considered semi-factive, does not project more from under negation than the other three operators. The pattern observed for {\em know} does not fit into either category.
	%

	%

@@

\noindent {\bf Discussion.}
	Our results---that projection is modulated by entailment-canceling operators and that there is by-predicate variation in the effect of operator on projection---are not captured by contemporary projection analyses, for several reasons.
	%
	The first is that contemporary analyses do not lead us to expect interactions with different types of entailment-cancelling operators. In \citet{heim_projection_1983}, for instance, the CC of (semi-)factive predicates projects to the global context, except when that would produce an inconsistency, in which case the CC is accommodated to the local context of the operator. While it is conceivable for the meaning of the operator to systematically interact with the possibility of local accommodation, no such interaction has been spelled out.
	%
	The second reason is that many contemporary analyses do not make predictions for the projection of the CC of many of the 20 predicates, as they are limited to (semi-)factive predicates, whose CCs are analyzed as presuppositions (e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992}), or entailed CCs that project unless at-issue with respect to the Question Under Discussion (e.g., \citealt{abrusan_predicting_2011,simons_best_2017}). A possible exception is the analysis of \citealt{schlenker_triggering_2021}, which predicts the potential for projection for CCs that are contextually entailed. In a full talk, we would like to discuss how this analysis might be extended to capture the gradient projection observed in our experiment.
	%
	The third reason is that contemporary projection analyses do not make sufficiently fine-grained distinctions between different clause-embedding predicates (but only between whether the CC is a presupposition or entailed). Consequently, they do not make predictions about the by-predicate variation in the effect of operator on projection.

% \noindent {\bf Discussion:  Empirical implications and lexical properties.}
	%
	Our results further question \posscite{karttunen_observations_1971} proposed difference between factive and semi-factive predicates (see also \citealt{beaver_have_2010}).
	Future research appealing to these categories must clarify their definition. Additionally, claims about projection variability must be relativized to the entailment-canceling operator.
	% Although our data replicate the result from \citet{tonhauser_how_2018} that, in polar questions, the CC of \emph{discover} is less projective than that of \emph{know}, the same does not hold in conditionals.
	%
	Finally, our results provide further support (from negation, modals, and conditionals) for the result of \citet{degen_are_2022}, that projection does not categorically differentiate between (semi-)factive and non-factive predicates: The CCs of \emph{inform} and \emph{acknowledge}, for instance, are at least as projective as that of some (semi-)factive predicates.
	%
	% Further, the variability we found is gradient, confirming previous research that by-predicate variability is not determined by categorical lexical classes (\citealt{tonhauser_how_2018,degen_are_2022}),
	% and extending this result to by-predicate variability in interaction with entailment-cancelling contexts.
	%
	In spite of a lack of categorical distinctions about the projection behavior of our verbs, we can find some interesting initial generalizations over lexical properties, indicated in \textbf{Figure\ 2}.

@@

\noindent

\newpage
{\scriptsize
\noindent {\bf (Selected) References:}
%
{\bf Abrusán (2011).} Predicting the presuppositions of soft triggers. {\em Linguistics and philosophy.} ~\textbullet~
% {\bf Beaver (2010).} Have you noticed that your belly button lint colour is related to the colour of your clothing? {\em Presuppositions and Discourse: Essays offered to Hans Kamp.}~\textbullet~
{\bf Degen \& Tonhauser (2022).} Are there factive predicates? An empirical investigation. {\em Language.}~\textbullet~
{\bf Djärv \& Bacovcin (2017).} Prosodic effects on factive presupposition projection. {\em Semantics and Linguistic Theory.}~\textbullet~
% {\bf Djärv, Zehr \& Schwarz (2018).} Cognitive vs. emotive factives: An experimental differentiation. {\em Proceedings of Sinn und Bedeutung.}~\textbullet~
{\bf Heim (1983).} On the Projection Problem for Presuppositions. {\em Proceedings of the Second West Coast Conference on Formal Linguistics.}~\textbullet~
% {\bf Hooper \& Thompson (1973).} On the applicability of root transformations. {\em Linguistic Inquiry.} ~\textbullet~
{\bf Karttunen (1971).} Some observations on factivity. {\em Research on Language \& Social Interaction.} ~\textbullet~
% {\bf Mahler (2020).} The social component of projection behavior of clausal complements. {\em Linguistic Society of America.}~\textbullet~
% {\bf van der Sandt (1992).} Presupposition projection as anaphora resolution. {\em Journal of Semantics.}~\textbullet~
{\bf Schlenker (2021).} Triggering presuppositions. {\em Glossa: A Journal of General Linguistics.}~\textbullet~
{\bf Sieker \& Solstad (2022).} Projective variability of (semi) factive verbs in family of sentence contexts: A rating study. {\em Proceedings of the 23rd Amsterdam Colloquium.}~\textbullet~
% {\bf Simons, Beaver, Roberts \& Tonhauser (2017).} The best question: Explaining the projection behavior of factives. {\em Discourse processes.}~\textbullet~
{\bf Smith and Hall (2014).} The relationship between projection and embedding environment. {\em Proceedings of the 48th Meeting of the Chicago Linguistics Society.}~\textbullet~
{\bf Tonhauser (2020).} Projection variability in Paraguayan Guaraní. {\em Natural Language \& Linguistic Theory.}~\textbullet~
{\bf Tonhauser, Beaver, \& Degen (2018).} How projective is projective content? Gradience in projectivity and at-issueness. {\em Journal of Semantics.}
% {\bf Tönnis (2021).} {\em German es-clefts in discourse. A question-based analysis involving expectedness.} Doctoral dissertation, Graz University.
% {\bf Zimmermann (2011).} {\em The grammatical expression of focus in West Chadic: Variation and uniformity in and across languages.} Walter de Gruyter.

\begin{figure}[h]
	\vspace{-.5\baselineskip}
	\centering
	\scalebox{.9}{\includegraphics[width=\textwidth]{graphs/proj-by-both.pdf}}\vspace{-1.8\baselineskip}
	\caption{\small Mean certainty ratings by predicate and operator with 95\% bootstrapped confidence intervals. Embedding operator coded by letter and color:  \texttt{N} (orange): negation, \texttt{M} (black): modals, \texttt{C} (green): conditional antecedents, \texttt{Q} (blue): polar questions.}
	\label{fig:figure1}
\end{figure}

\begin{table}[h]
	\vspace{-1\baselineskip}\phantom{.}
	\centering
	\hspace{-1.3em}
	\begin{tabular}{p{.65\linewidth} p{.31\linewidth}}
		\scalebox{.75}{
			\begin{tabular}{llrrrr}
				Model & & Estimate & Std. Error & t-value\\
				\midrule
				\#1 & Intercept: \emph{question} & 0.51 & 0.01 & 44.78 & ***\\
				& operator: conditional & 0.05 & 0.01 & 5.30 & ***\\
				& operator: modal & -0.04 & 0.01 & -4.45 & ***\\
				& operator: negation & -0.03 & 0.01 & -4.67 & ***\\
				\midrule
				\#2 & Intercept: \emph{\bf be annoyed}/negation & 0.87 & 0.01 & 79.86 & ***\\
				& operator: conditional & -0.12 & 0.02  & -7.36 & ***\\
				& operator: modal & -0.16 & 0.02  & -10.01 & ***\\
				& operator: question & 0.02 & 0.01 & 1.72 & n.s.\\
				\midrule
				\#3 & Intercept: \emph{\bf discover}/negation & 0.68 & 0.01 & 62.70 & ***\\
				& operator: conditional & 0.11 & 0.02 & 7.11 & ***\\
				& operator: modal & -0.06 & 0.02 & -3.63 & ***\\
				& operator: question & 0.10 & 0.01 & 7.08 & ***\\
				\midrule
				\#4 & Intercept: \emph{\bf know}/negation & 0.79 & 0.01 & 72.97 & ***\\
				& operator: conditional & 0.00 & 0.02 & -0.06 & n.s.\\
				& operator: modal & -0.14 & 0.02 & -9.18 & ***\\
				& operator: question & 0.08 & 0.01 & 5.67 & ***\\
				\bottomrule
			\end{tabular}
		}
		&
		\parbox{\linewidth}{\caption{\small Excerpt of the output from three linear mixed effects models; \textbf{\#1} has fixed effects of operator; random effects: participant and item intercepts, \textbf{\#2-4} have fixed effect: operator, predicate, and their interaction; random effect: participant intercepts.
		Models were fit with \texttt{lme4, lmertest} in \texttt{R}. Models \textbf{\#2--4} also had at least $34$ highly significant interaction terms of \texttt{operator} and \texttt{predicate} with $p < 0.001$ (not shown here).}\label{t:models}}

	\end{tabular}
\end{table}

\hspace{-2.7em}
	\begin{minipage}{\textwidth}\centering
	\begin{tabular}{p{.235\linewidth} p{.235\linewidth} p{.235\linewidth} p{.235\linewidth}}
		\parbox{\linewidth}{\centering (a) \textbf{Negation high}\\
		\includegraphics[width=.26\textwidth]{graphs/profile1.pdf}}
		&
		\parbox{\linewidth}{\centering (b) \textbf{Negation low}\\
		\includegraphics[width=.26\textwidth]{graphs/profile4.pdf}}
		&
		\parbox{\linewidth}{\centering (c) \textbf{Conditional high}\\
		\includegraphics[width=.26\textwidth]{graphs/profile2.pdf}}
		&
		\parbox{\linewidth}{\centering (d) \textbf{Modal low}\\
		\includegraphics[width=.26\textwidth]{graphs/profile5.pdf}}
	\end{tabular}
\end{minipage}

\vspace{-.4\baselineskip}
\noindent \small Figure 2: \small Mean certainty ratings by operator (\texttt{M}: Modal, \texttt{N}: Negation, \texttt{Q}: Polar Question, \texttt{C}: Conditional antecedent) with 95\% bootstrapped confidence intervals, for some groups of predicates (\lq predicate patterns\rq).

>>>>

\documentclass[11pt, a4paper]{article}

@@

\usepackage{euler} % math font package needs to be loaded before others
\usepackage{xunicode,xltxtra, polyglossia}
\setdefaultlanguage[variant=american]{english}

@@

%% decoration and features
	%%% colors
	\usepackage[dvipsnames]{xcolor}
	\definecolor{orangee}{HTML}{E69F00}
	\definecolor{greenn}{HTML}{009E73}
	\definecolor{bluee}{HTML}{56B4E9}

	%% fonts
	\setmainfont[Scale=MatchLowercase,Mapping=tex-text, SmallCapsFeatures={Letters=SmallCaps}]{Arial}
	\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Arial}
	\setmonofont[Scale=MatchLowercase]{Andale Mono}

@@

\begin{center}
	\textbf{\large%\thetitle
		Projection variability of complement clauses across different operators}
\end{center}

\paragraph{Short summary:} % (fold)
	We examine how the content of embedded complement clauses projects across different entailment-canceling operators for various clause-embedding predicates.
	%
	We measured projection for 20 predicates across four operators: polar questions, negation, modals, and conditionals. Results reveal projection variation by operator and by-predicate variation in the effect of operator on projection.
	%
	Existing theoretical accounts of projection (e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992,abrusan_predicting_2011,schlenker_triggering_2021}) do not capture the observed variability.
	%
	Our findings highlight the importance of considering interactions between predicates and operators and generate important questions for future research on projection.

% paragraph short_summary (end)

\paragraph{Projection across entailment-cancelling operators.}
	Interpreters may infer that a speaker uttering a sentence with an embedded complement clause \ref{ex:family} is committed to the content of the complement (CC, here: \emph{Julian dances salsa,})
	even when embedded under an entailment-canceling operator \Next[a-d]. Then we say that the CC \emph{projects}.

	\ex. \label{ex:family}
		\a. \label{ex:q}
			{\bf Polar Question:} \hfill
			\emph{Did Cole discover that Julian dances salsa?}
		\b. \label{ex:neg}
			{\bf Negation:} \hfill
			\emph{Cole didn't discover that Julian dances salsa.}
		\c. \label{ex:mod}
			{\bf Modal:} \hfill
			\emph{Perhaps Cole discovered that Julian dances salsa.}
		\d. \label{ex:cond}
			{\bf Conditional:} \hfill
			\emph{If Cole discovered that Julian dances salsa, Logan will be joyful.}
		\z.
	\z.

	\noindent
	Previous research has investigated projection variability across these operators only rarely, and with conflicting findings.
	%
	For English clause-embedding predicates, \citet{karttunen_observations_1971} proposed a distinction between factives (e.g., \emph{be annoyed, regret}), where the CC projects across all four operators, and semi-factives (e.g., \emph{discover, realize, see, notice}) where it always projects across negation, but not always across the other operators.
	%
	\cite{sieker_projective_2022}, investigating the projection of German clause-embedding predicates across these operators, found an overall pattern of more projection across negation than the others, but no operator/predicate interaction effect.
	%
	%
	In contrast, \citet{smith_relationship_2014} found different projectivity patterns for different types of English projective contents: That of epithets and the CC of \emph{know} were more projective under negation than conditionals, whereas that of non-restrictive relative clauses and \emph{win} showed the opposite pattern.
	%

	Because the studies diverge about whether they find operator/predicate interaction effects, the question arises whether they differ due to cross-linguistic variation, task differences, or different types of contents being tested. To address this, we conducted a series of experiments designed to assess projection across the four entailment-canceling operators in \ref{ex:family}. We used the same projection measure as \citet{sieker_projective_2022} (the `certain that' diagnostic; see e.g., \citealp{tonhauser_how_2018,djarv_prosodic_2017,mahler_social_2020}) and applied it to the CC of 20 English clause-embedding predicates, including factive (\emph{be annoyed, know, reveal}) and semi-factive predicates (\emph{discover, see}),
	and 15 non-factive predicates, given recent findings that their complements may also project, albeit to varying degrees (\citealt{degen_are_2022}).

\paragraph{Method.}
	Projection of the CC of the 20 clause-embedding predicates was measured in four sets of experiments: Predicates were embedded in polar questions in Exps.\ 1, under negation (Exps.\ 2), under a modal {\em perhaps} (Exps.\ 3), and in conditional antecedents (Exps.\ 4). (Each set contained three experiments using different at-issueness measures in a separate block. Here, we focus on the projection ratings.)
	%
	Participants read utterances like in \ref{ex:family} and rated whether the speaker (who was named) was certain of the CC (e.g.: \emph{\lq Is [the speaker] certain that Julian dances salsa?\rq}), on a slider marked \emph{`no'} (coded as \texttt{0}) at one end and \emph{`yes'} (coded as \texttt{1}) on the other. Each participant saw all 20 clause-embedding predicates (each with a unique content from a set of 20) under one operator. We analyze data from $2,682$ self-reported native speakers of American English, recruited on Prolific or Amazon's MT platform.

\begin{figure}[ht]
	\vspace{-.5\baselineskip}
	\centering
	\includegraphics[width=\textwidth]{graphs/proj-by-both.pdf}
	\caption{\small Mean certainty ratings by predicate and operator with 95\% bootstrapped confidence intervals. Entailment-cancelling operator coded by letter and color:  \textcolor{orangee}{\texttt{N}: negation}, \texttt{M}: modals, \textcolor{greenn}{\texttt{C}: conditional antecedents}, \textcolor{bluee}{\texttt{Q}: polar questions}.}
	\label{fig:figure1}
\end{figure}

\paragraph{Results and Analysis.}
	Our analysis reveals two key results: \textbf{(i)} There is projection variability by operator, with higher mean projection ratings for question-operators (Maximum likelihood estimate: $0.51$) than negation (MLE: $0.48$) and modals ($0.47$), but lower than for conditional antecedents ($0.56$, see model \#1 in Table\ \ref{t:models}).
	%
	This differs from \posscite{sieker_projective_2022} observation that the CC of German clause-embedding predicates projects more across negation than the other operators, suggesting potential cross-linguistic variation in the projection of clausal complements across entailment-canceling operators.

	\textbf{(ii)} There is by-predicate variation in the effect of operator on projection, as illustrated in Figure~\ref{fig:figure1}, showing mean projection ratings for the 20 clause-embedding predicates by operator, with predicates ordered by their mean rating across operators (\emph{be annoyed} has the highest overall mean).
	%
	For instance, the CC of \emph{be annoyed} projects more across negation and questions than conditionals and modals, and the CC of \emph{discover} projects less across negation than conditionals and questions, but more across negation than modals. The CC of \emph{know} projects less across negation than questions, but more across negation than modals, while the difference between negation and conditionals is not significant.
	%
	These generalizations are supported by models\ \# 2--4 in Table\ \ref{t:models}, which also each have at least $34$ highly significant interaction terms (out of $57$ possible interactions of operator and predicate).
	%

	Our finding of operator/predicate-interactions concurs with \citet{smith_projection_2011}, but we did not reproduce their result that the CC of \emph{know} projects more from negation than conditionals.
	%
	Further, our finding differs from the result of \citet{sieker_projective_2022}, who found no interaction between predicates and operators. Given that the methods and the set of projective contents of our experiment were very similar to theirs, this may suggest cross-linguistic variation in projection variability (cf. \citealt{tonhauser_projection_2020}).
	%
	Additionally, our results are contradict \posscite{karttunen_observations_1971} distinction between factive and semi-factive predicates: The CC of (factive) \emph{be annoyed} does not project invariably across four operators, and the CC of \emph{discover,}  considered semi-factive, does not project more from under negation than the other three operators. The pattern observed for {\em know} does not fit into either category.

@@

\paragraph{Discussion.}
	Our results---that various entailment-canceling operators affect projection differently and that there is by-predicate variation in the effect of operator on projection---are not captured by contemporary projection analyses, for several reasons.
	%
	First, they do not predict variation associated with different types of entailment-cancelling operators. In \citet{heim_projection_1983}, for instance, the CC of (semi-)factive predicates projects to the global context, except when that would produce an inconsistency and the CC is accommodated locally. While it is conceivable for operator meanings to systematically affect the possibility of local accommodation, this has not been spelled out.
	%
	The second reason is that many analyses only focus on (semi-)factive predicates, whose CCs are analyzed as presuppositions (e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992}), or entailed CCs that project unless at-issue with respect to the Question Under Discussion (e.g., \citealt{abrusan_predicting_2011,simons_best_2017}). This limits their predictive power for other predicates.
	%
	\posscite{schlenker_triggering_2021} may be an exception, which predicts the potential of projection for CCs that are contextually entailed. In the full paper, we discuss how Schlenker's analysis may be extended to capture the gradient projection observed in our experiment.
	%
	Finally, no current analysis makes sufficiently fine-grained distinctions between different clause-embedding predicates (but only between whether the CC is presupposed/entailed or not). Consequently, precluding predictions about the by-predicate variation in operator effects.

	Our results further question \posscite{karttunen_observations_1971} proposed distinction between factive and semi-factive predicates (see also \citealt{beaver_have_2010,sieker_projective_2022}).
	Future research appealing to these categories must clarify their definition. 
	% Additionally, claims about projection variability must be relativized to the entailment-canceling operator.
	% Although our data replicate the result from \citet{tonhauser_how_2018} that, in polar questions, the CC of \emph{discover} is less projective than that of \emph{know}, the same does not hold in conditionals.
	%
	Finally, our results provide further support (from negation, modals, and conditionals) for the result of \citet{degen_are_2022}, that projection does not categorically differentiate between (semi-)factive and non-factive predicates: The CCs of \emph{\lq inform\rq} and \emph{\lq acknowledge\rq}, for instance, are at least as projective as those of some (semi-)factive predicates.
	%
	% Further, the variability we found is gradient, confirming previous research that by-predicate variability is not determined by categorical lexical classes (\citealt{tonhauser_how_2018,degen_are_2022}),
	% and extending this result to by-predicate variability in interaction with entailment-cancelling contexts.
	%
	In a full presentation, we would discuss how more fine-grained lexical distinctions may affect projection variability: For example, the CCs of \emph{\lq think\rq} and \emph{\lq pretend\rq} (which are often used anti-veridically) project more across negation than other operators. The CCs of \emph{\lq reveal, confess, admit\rq} and \emph{\lq announce\rq} (communicative achievement predicates) project most from conditional antecendents.

@@

\begin{table}[h]
	\centering
	\begin{tabular}{llrrrr}
		Model & & Estimate & Std. Error & t-value\\
		\midrule
		\#1 & Intercept: \emph{question} & 0.51 & 0.01 & 44.78 & ***\\
		& operator: conditional & 0.05 & 0.01 & 5.30 & ***\\
		& operator: modal & -0.04 & 0.01 & -4.45 & ***\\
		& operator: negation & -0.03 & 0.01 & -4.67 & ***\\
		\midrule
		\#2 & Intercept: \emph{\bf be annoyed}/negation & 0.87 & 0.01 & 79.86 & ***\\
		& operator: conditional & -0.12 & 0.02  & -7.36 & ***\\
		& operator: modal & -0.16 & 0.02  & -10.01 & ***\\
		& operator: question & 0.02 & 0.01 & 1.72 & n.s.\\
		\midrule
		\#3 & Intercept: \emph{\bf discover}/negation & 0.68 & 0.01 & 62.70 & ***\\
		& operator: conditional & 0.11 & 0.02 & 7.11 & ***\\
		& operator: modal & -0.06 & 0.02 & -3.63 & ***\\
		& operator: question & 0.10 & 0.01 & 7.08 & ***\\
		\midrule
		\#4 & Intercept: \emph{\bf know}/negation & 0.79 & 0.01 & 72.97 & ***\\
		& operator: conditional & 0.00 & 0.02 & -0.06 & n.s.\\
		& operator: modal & -0.14 & 0.02 & -9.18 & ***\\
		& operator: question & 0.08 & 0.01 & 5.67 & ***\\
		\bottomrule
	\end{tabular}
	\caption{\small Excerpt of the output from three linear mixed effects models; \textbf{\#1} has fixed effects of operator; random effects: participant and item intercepts, \textbf{\#2-4} have fixed effect: operator, predicate, and their interaction; random effect: participant intercepts.
		Models were fit with \texttt{lme4, lmertest} in \texttt{R}. Models \textbf{\#2--4} also had at least $34$ highly significant interaction terms of \texttt{operator} and \texttt{predicate} with $p < 0.001$ (not shown here).}\label{t:models}
\end{table}

% \hspace{-2.7em}
% 	\begin{minipage}{\textwidth}\centering
% 	\begin{tabular}{p{.5\linewidth} p{.5\linewidth}}
% 		\parbox{\linewidth}{\centering (a) \textbf{Negation high}\\
% 		\includegraphics[width=.8\linewidth]{graphs/profile1.pdf}}
% 		&
% 		\parbox{\linewidth}{\centering (b) \textbf{Negation low}\\
% 		\includegraphics[width=.8\linewidth]{graphs/profile4.pdf}}
% 		\\
% 		\parbox{\linewidth}{\centering (c) \textbf{Conditional high}\\
% 		\includegraphics[width=.8\linewidth]{graphs/profile2.pdf}}
% 		&
% 		\parbox{\linewidth}{\centering (d) \textbf{Modal low}\\
% 		\includegraphics[width=.8\linewidth]{graphs/profile5.pdf}}
% 		\\
% 	\end{tabular}
% \end{minipage}

% \vspace{-.4\baselineskip}
% \noindent \small Figure 2: \small Mean certainty ratings by operator (\texttt{M}: Modal, \texttt{N}: Negation, \texttt{Q}: Polar Question, \texttt{C}: Conditional antecedent) with 95\% bootstrapped confidence intervals, for some groups of predicates (\lq predicate patterns\rq).
